The first high-redshift changing-look quasars

### 2020-06-12 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
updating CIV_CLQs_rv1

Proper comparison of the spectra requires reliable flux calibrations,
which is a challenge since not all data were taken in photometric
conditions.  SDSS spectra are spectrophotometrically calibrated.  BOSS
and eBOSS spectra have spectrophotometric corrections applied in the
latest data release \citep{Hutchinson2016, Jensen2016, Margala2016}.
However, some of the Palomar and Keck data suffered from variable
conditions and clouds.  For lower redshift AGN, the narrow \oiii
emission line is typically used to align spectrophotometry since it is
spatially extended and not expected to change significantly on human
timescales \citep[e.g.,][]{Barth2011}. However, due to the
high-redshift of our quasars, \oiii is not available to us to use for
scaling the spectra.  Instead, we use photometric data from ZTF since
our Palomar and Keck data were all taken after MJD 57500.  This
provides broad-band photometry at the time of the spectroscopy, which
we use to scale the spectra whose initial calibration is based on
spectrophotometric standards observed on the same nights.
{\bf We note the resulting uncertainty in flux calibration is 2-5\%.
  This uncertainty is not propagated into measurements. 
}

@@

In particular, we use the Quasar Spectral Fitting (QSFit) software
package presented in \citet{Calderone2017}. This provides luminosity
estimates as well as width, velocity offset and EW of 20 emission
lines, including \civ, \ciii, and \mgii.  We process and fit all nine
spectra using the lastest version (v1.3.0) of the QSFit
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
calculator}. The host galaxy and blended iron emission at rest-frame
optical wavelengths components are automatically disabled when they
can not be constrained by the available data, as is the case for all
our quasars.  Power-law continuum slopes, $\alpha$, where $f_{\lambda}
\propto \lambda^{\alpha}$, are also reported in these catalogues and
from QSFit.

{\bf As described in detail in \citet{Calderone2017}, the
uncertainties in the measured quantities are determined by two
methods; a Fisher matrix method and a Monte Carlo resampling method.
Due to correlations among model parameters, e.g. emission-line
luminosities and widths, the Fisher matrix method likely
underestimates the errors.  However, upon investigation, the
parameters of the involved model components (a power-law for the
continuum, and a single Lorentzian profile for the emission lines)
show negligible correlations, hence we use the Fisher matrix method
to estimate the uncertainties on the model parameters.  Section 2.8.3
and Appendix B4 of \citet{Calderone2017} gives further details and
compares the Fisher matrix and Monte Carlo resampling uncertainties
and distributions.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Photometric and Overall Spectral Evolution}
Figure~\ref{fig:civ_clqs_LCs} presents the optical and mid-infrared light
curves for three high-redshift CLQ quasars.  Figure~\ref{fig:civ_clqs_LCs}
also indicates the spectra for each epoch with vertical dashed lines
in the light curves.

Figure~\ref{fig:civ_clqs_J12_spec} shows the rest-frame spectra for SDSS J1205+3422.
For J1205+3422, our spectral observations cover 5195 observed days,
corresponding to 1691 days in the rest-frame. This quasar was
initially identified in SDSS in 2005 May as a bright, $g \approx
18.0$, blue-sloped quasar with broad Si\,{\sc iv}/O\,{\sc iv}, \civ,
C\,{\sc iii}, and Mg\,{\sc ii}. \ciii\ and \civ\ have large
blueshifts, $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km s$^{-1}$,
respectively.  By 2019, however, the optical brightness dropped by
nearly 2 magnitudes and the spectra are significantly less blue.  \lya
and \nv are detectable in both 2019 spectra, but is just blueward of
the wavelength range covered by the original SDSS spectrum. The \civ\
and \ciii\ lines have faded significantly between the SDSS observation
in 2005 and the Palomar observations in 2019.  Note that \civ\ is
extremely faint in the 2019 February spectrum, but that night suffered
from poor conditions.

Figure~\ref{fig:civ_clqs_J16_spec} shows the rest-frame spectra for SDSS J1638+2827.
For J1638+2827, our spectral observations cover 4030 observed days,
corresponding to 1265 days in the rest-frame. Here, in the initial
epoch spectrum, \civ\ is broad and bright, as is C\,{\sc
iii}. However, $\approx$400 rest-frame days later, the broad \civ\ and
\ciii\ emission lines have faded, the continuum slope around 1400\AA\
has changed from $\approx-1.48$ to $\approx-2.25$, but the \lya/\nv
emission complex is very similar in shape {\bf and intensity}. Around
870 days in the rest-frame after the second spectral epoch, at the
time of the third spectral epoch, the source has brightened from
optical magnitudes of $\sim 20$ mag to $\sim 18.5$ mag. Ly$\alpha$,
N\,{\sc v}, \civ, \ciii, and \mgii\ are all apparent and broad, with
\mgii\ being seen for the first time at high signal-to-noise. An
absorption feature between \lya and \nv is seen in all three spectral
epochs.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
    \vspace{-18pt}
  \caption{Observed spectra and best fit models of the \civ\ spectral region.
    The solid blue line is the Lorentzian profile fit to the \civ\ emission line.
    The long-dashed red line is the continuum fit, with the solid orange
    line giving the overall fit. The short-dashed vertical lines gives the
    rest wavelengths of the \civ\ doublet. }
  \label{fig:QSFit-CIV}
\end{figure}

\subsection{\civ\ Emission Line Evolution}
We analyzed the multi-epoch spectra of the three quasars using the
QSFit spectral fitting package \citep{Calderone2017}.  One advantage
of using QSFit is that it allows constraints on the slope and
luminosity of the broad band continuum of the source. The relevant
estimated quantities, including continuum luminosity and slope at
rest-frame 1450\AA, \civ\ line luminosity, FWHM, and EW are given in
Table~\ref{tab:QSFit-results}.
{\bf 
All fits are obtained by taking the Milky Way extinction
\citep{Schlafly2011} into account.  The extinction values are: $E(B-V)
=0.013$ for J1205+3422; $E(B-V) =0.034$ for J1638+2827 and $E(B-V)
=0.041$ for J2228+2201.  as taken from NED (e.g. for
\href{http://ned.ipac.caltech.edu/cgi-bin/objsearch?search_type=Near+Position+Search&in_csys=Equatorial&in_equinox=J2000.0&lon=12%3A05%3A44.7&lat=%2B34%3A22%3A52.4&radius=0.1&hconst=73&omegam=0.27&omegav=0.73&corr_z=1&z_constraint=Unconstrained&z_value1=&z_value2=&z_unit=z&ot_include=ANY&nmp_op=ANY&out_csys=Equatorial&out_equinox=J2000.0&obj_sort=Distance+to+search+center&of=pre_text&zv_breaker=30000.0&list_limit=5&img_stamp=YES#GalacticExtinction_0}{J1205+3422}).
}
The best fit models
in the region of the \civ\ emission line are shown in
Figure~\ref{fig:QSFit-CIV}.

@@

@@

\begin{table}
  \centering
  \begin{tabular}{l l l r}
    \hline
    \hline
    Object       & MJD & $L_{\rm bol}$&  $\eta_{\rm Edd}$  \\
    \hline
                     & 53498 & 47.22     &  $-$0.61   \\
 J1205+3422 & 58538 &  46.07    &   $-$1.76  \\   %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
                     & 58693 &  46.57    &  $-$1.26  \\                    
    \hline 
                     & 54553 & 46.17   & $-$1.03  \\
J1638+2827  & 55832 & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
                     & 58583 & 46.50   & $-$0.69   \\
    \hline 
                     & 56189  & 46.23  &  $-$1.24 \\
J2228+2201  & 56960 & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
                     & 58693 & 46.83   &  $-$0.64 \\
    \hline
    \hline
  \end{tabular}
  \caption{Bolometric luminosities are given in either \citet{Shen2011} or
    \citet{Kozlowski2017} for the three CLQs. We scale these values using
    our measured $\nu L_{\nu}$ continuum luminosity values.  From
    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}

>>>>

Proper comparison of the spectra requires reliable flux calibrations,
which is a challenge since not all data were taken in photometric
conditions.  SDSS spectra are spectrophotometrically calibrated.  BOSS
and eBOSS spectra have spectrophotometric corrections applied in the
latest data release \citep{Hutchinson2016, Jensen2016, Margala2016}.
However, some of the Palomar and Keck data suffered from variable
conditions and clouds.  For lower redshift AGN, the narrow \oiii
emission line is typically used to align spectrophotometry since it is
spatially extended and not expected to change significantly on human
timescales \citep[e.g.,][]{Barth2011}. However, due to the
high-redshift of our quasars, \oiii is not available to us to use for
scaling the spectra.  Instead, we use photometric data from the ZTF
since our Palomar and Keck data were all taken after MJD 57500.  This
provides broad-band photometry at the time of the spectroscopy, which
we use to scale the spectra whose initial calibration is based on
spectrophotometric standards observed on the same nights.  {\bf We
note the resulting uncertainty in flux calibration is 2-5\%.  This
uncertainty is not propagated into measurements.}

@@

In particular, we use the Quasar Spectral Fitting (QSFit) software
package presented in \citet{Calderone2017}. This provides luminosity
estimates as well as width, velocity offset and EWs of 20 emission
lines, including \civ, \ciii, and {Mg\,{\sc ii}}. We process and fit
all nine spectra (3 quasars with 3 epochs) using the lastest version
(v1.3.0) of the QSFit
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online
calculator}. The host galaxy and blended iron emission at rest-frame
optical wavelengths components are automatically disabled when they
can not be constrained by the available data, as is the case for all
our quasars.  Power-law continuum slopes, $\alpha$, where $f_{\lambda}
\propto \lambda^{\alpha}$, are also reported in these catalogues and
from QSFit.

{\bf As described in \citet{Calderone2017}, the uncertainties in the
measured quantities are determined by two methods; a Fisher matrix
method and a Monte Carlo resampling method.  One might expect
correlations among model parameters, e.g. emission-line luminosities
and widths, and thus the Fisher matrix method to underestimates the
errors.  However, upon investigation, the parameters of the involved
model components (a power-law for the continuum, and a single
Lorentzian profile for the emission lines) show negligible
correlations, hence we use the Fisher matrix method to estimate the
uncertainties on the model parameters.  Section 2.8.3 and Appendix B4
of \citet{Calderone2017} gives further details and compares the Fisher
matrix and Monte Carlo resampling uncertainties and distributions.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Photometric and Overall Spectral Evolution}
Figure~\ref{fig:civ_clqs_LCs} presents the optical and mid-infrared light
curves for three high-redshift CLQ quasars.

Figure~\ref{fig:civ_clqs_J12_spec} shows the rest-frame spectra for
SDSS J1205+3422.  For J1205+3422, our spectral observations cover 5195
observed days, corresponding to 1691 days in the rest-frame. This
quasar was initially identified in SDSS in 2005 May as a bright, $g
\approx 18.0$, blue-sloped quasar with broad Si\,{\sc iv}/O\,{\sc iv},
\civ, C\,{\sc iii}, and Mg\,{\sc ii}.  \civ\ has a blueshift of
$\approx$580$\pm$80 km s$^{-1}$.  By 2019, however, the optical
brightness dropped by nearly 2 magnitudes and the spectra are
significantly less blue.  \lya and \nv are detectable in both 2019
spectra, but is just blueward of the wavelength range covered by the
original SDSS spectrum. The \civ\ and \ciii\ lines have faded
significantly between the SDSS observation in 2005 and the Palomar
observations in 2019.  Note that \civ\ is extremely faint in the 2019
February spectrum, but that night suffered from poor conditions.

Figure~\ref{fig:civ_clqs_J16_spec} shows the rest-frame spectra for
SDSS J1638+2827.  For J1638+2827, our spectral observations cover 4030
observed days, corresponding to 1265 days in the rest-frame. Here, in
the initial epoch spectrum, \civ\ is broad and bright, as is C\,{\sc
iii}. However, $\approx$400 rest-frame days later, the broad \civ\ and
\ciii\ emission lines have faded, the continuum slope around 1400\AA\
has changed from $\approx-1.16$ to $\approx-2.17$, but the \lya/\nv
emission complex is very similar in shape {\bf and intensity}. Around
870 days in the rest-frame after the second spectral epoch, at the
time of the third spectral epoch, the source has brightened from
optical magnitudes of $\sim$20 mag to $\sim$18.5 mag. Ly$\alpha$,
N\,{\sc v}, \civ, \ciii, and \mgii\ are all apparent and broad, with
\mgii\ being seen for the first time at high signal-to-noise. An
absorption feature between \lya and \nv is seen in all three spectral
epochs.

@@

\begin{figure*}
  \centering
  \includegraphics[width=18.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
    \vspace{-18pt}
  \caption{Observed spectra and best fit models of the \civ\ spectral region.
    The solid blue line is the Lorentzian profile fit to the \civ\ emission line.
    The long-dashed red line is the continuum fit, with the solid orange
    line giving the overall fit. The short-dashed vertical lines gives the
    rest wavelengths of the \civ\ doublet. }
  \label{fig:QSFit-CIV}
\end{figure*}

\subsection{\civ\ Emission Line Evolution}
We analyse the multi-epoch spectra of the three quasars using the
QSFit spectral fitting package \citep{Calderone2017}.  One advantage
of using QSFit is that it allows constraints on the slope and
luminosity of the broad band continuum of the source. The relevant
estimated quantities, including continuum luminosity and slope at
rest-frame 1450\AA, \civ\ line luminosity, FWHM, and EW are given in
Table~\ref{tab:QSFit-results}.  {\bf All fits are obtained by taking
the Milky Way extinction \citep{Schlafly2011} into account.  The
extinction values are: $E(B-V) =0.013$ for J1205+3422; $E(B-V) =0.034$
for J1638+2827 and $E(B-V) =0.041$ for J2228+2201.  as taken from the
\href{http://ned.ipac.caltech.edu/}{NASA/IPAC Extragalactic Database} 
}. The best fit models in the region of the \civ\ emission line are
shown in Figure~\ref{fig:QSFit-CIV}.

@@

{\bf The values in Table~\ref{tab:QSFit-results} are
$\approx$0.27-0.30 dex higher than the estimates in
Table~\label{tab:Eddington_ratios}, which is to be expected given the
difference of calibrations factors. In fact, the virial products are
all remarkably constant and compatible with a single black hole mass
estimate, within the standard 0.5 dex uncertainty, across the 3 epochs
for all the quasars.  This fact gives us confidence in the line
fitting methods.}

@@

\begin{table}
  \centering
  \begin{tabular}{l l  cc    l     r}
    \hline
    \hline
\multirow{2}{*}{Object} & \multirow{2}{*}{MJD} & $\log (M/M_{\odot})$ &  $\log (M/M_{\odot})$ & log($L_{\rm bol}$) &  \multirow{2}{*}{$\eta_{\rm Edd}$}  \\
                                    &                                  &    QSFit                     &   Liter. value                &                             &    \\
    \hline
                                    & 53498                        &    9.39                      &  9.49$\pm$0.04$^{\dagger}$   &   47.22                  &  $-$0.61   \\
 J1205+3422               & 58538                         &    9.78                     &   ---                                        &  46.07                  &   $-$1.76 \\  %% L_Edd (J12)  = 47.82637   for log(M) = 9.726
                                    & 58693                        &    9.39                      &                                                 &  46.57                &  $-$1.26  \\                    
    \hline 
                                    & 54553                        &   8.84                      &  8.74$\pm$0.15$\dagger$                     & 46.17   & $-$1.03  \\
J1638+2827                 & 55832                       &    8.80                             &    9.13                                         & 45.98   & $-$1.21  \\      %% L_Edd (J16)  = 47.191370  for log(M) = 9.091
                                    & 58583                        &   9.01                               &                          & 46.50   & $-$0.69   \\
    \hline 
                                     & 56189                       & 8.70                                & 8.73                         & 46.23  &  $-$1.24 \\
J2228+2201                 & 56960                       &   9.39                                &                         & 47.34  & $-$0.12  \\      %% L_Edd (J22)  = 47.466370  or log(M) = 9.366
                                     & 58693                      &  8.97                                &                         & 46.83   &  $-$0.64 \\
    \hline
    \hline
  \end{tabular}
  \caption{Virial Mass estimates, bolometric luminosities and Eddington ratios for the
    three quasars. 
    $\dagger$From \citet{Shen2011} SDSS DR7 Quasar catalog.
    $\dagger$From \citet{Shen2011} SDSS DR7 Quasar catalog.
    are given in either \citet{Shen2011} or
    \citet{Kozlowski2017} for the three CLQs. We scale these values using
    our measured $\nu L_{\nu}$ continuum luminosity values.  From
    Section~\ref{sec:BH_masses}, we assume: $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.726$ for J1205+3422; $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.091$ for J1638+2827, and $\log(M_{\rm BH,
      vir}/M_{\odot}) = 9.366$ for J2228+2201.  The Eddington luminosity
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}
